Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-24 sattose/paper.tex
Trying to write more background

There are already a few researches that look into refactoring opportunities for clone pairs \cite{}
%TODO: What are clone classes, what are clone instances, etc.

@@

\subsection{CloneRefactor}
A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection. For our tool we decided to combine AST and Graph based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs). We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code. We then collect each statement and declaration (ommitting their child statements and declarations) and compare those to find duplicates. This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of it's duplicates (verically). This is displayed in figure \ref{fig:clonerefactor}.

>>>>

A tool called DCRA (Duplicated Code Refactoring Advisor) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}. This tool chooses to only focus on refactoring clone pairs because they argue that \textit{clone pairs are much easier to manage when considered singularly.} As intermidiate steps the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation between code fragments in a clone pair in terms of inheritance.

@@

\subsection{CloneRefactor}
A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection. For our tool we decided to combine AST and Graph based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs). We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12). We collect each statement and declaration and compare those to find duplicates. This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of it's duplicates (verically). This is displayed in figure \ref{fig:clonerefactor}.
